Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2019-02-08 pkg/disttree/inst/draft/rejoinder2.Rnw
further comments and revisions based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2454 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 7bafc7f1c6ded64c069588aad011b416b311048d

\setkomavar{subject}{Revision of AOAS1804-015}

@@

Thank you very much for the positive and constructive feedback from you, 
the associate editor, and the two referees. Based on your comments, the
manuscript has been revised and we feel that this substantially improved our
contribution.
%
The most important changes are:
\begin{itemize}

\item \emph{Discussion.}\\
TO DO

\item \emph{\ldots}\\

% \item In the calculation of variable importance we have detected some inconsistencies.
% Thus, we have revised the applied method to evaluate this measurement and recalculated
% variable importance for the distributional forest.

\end{itemize}

All changes and additions are explained in much more detail in the
point-to-point reply on the next pages.

@@

\vspace*{-2.8cm}
\hspace*{-0.3cm} 
\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

@@

Thank you very much for your comment! East Tyrol lies in a different climat zone than the 
rest of Tyrol indicating different meteorological characteristics. For example, a covariate
might have a linear effect on the expected amount of rain in East Tyrol while it has a
non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
GAMLSS will capture this influence better than a tree model, particularly if this covariate
is correctly specified in the model (which might be the case in the prespecified GAMLSS).
Of course, these are just assumptions and there could be many other reasons. However,
looking at the results of the cross-validation in Supplement~B it can be observed that
the difference in performance between the GAMLSS and the distributional tree models as
seen in the single evaluation evens out, hence the specific choice of learning years seems
to have an impact as well.

@@

\begin{review}
The authors have well addressed the reviewers’ comments. The two added supplementary 
materials give a more solid ground to the proposed post-processing method by showing 
it is robustness to some choice of forecast distribution and that the results presented 
in the main manuscript does not hold only for the specific station.
I recommend the paper to be accepted after the minor revisions proposed
hereafter have been adressed.
\end{review}

@@

TO DO

Thank you very much for the positive and constructive 
comments regarding the paper.

>>>>

\setkomavar{subject}{Revision of AOAS1811-010}

@@

Thank you very much for the positive and constructive feedback from you, 
the associate editor, and the two referees. Based on your comments, the
manuscript has been revised. In particular, an additional subsection
has been added to the discussion commenting on the complexity of the
applied distributions.
%The most important changes are:
%\begin{itemize}
%\item \emph{Discussion.}\\
%\item \emph{\ldots}\\
%\end{itemize}
All changes and extensions are explained in much more detail in the
point-to-point reply on the next pages.

@@

%\vspace*{-2.8cm}
%\hspace*{-0.3cm} 
%\includegraphics[width = 0.23\textwidth]{signature-Schlosser}

@@

Thank you very much for your comment! East Tyrol lies in a different climate zone than the 
rest of Tyrol indicating different meteorological characteristics. For example, a covariate
might have a linear effect on the expected amount of rain in East Tyrol while it has a
non-additive effect in Northern Tyrol. In this case, in East Tyrol an additive model such as 
GAMLSS will capture this influence better than a tree model, particularly if this covariate
is correctly specified in the model (which might be the case in the prespecified GAMLSS).
Of course, these are just assumptions and there could be many other reasons. However,
looking at the results of the cross-validation in Supplement~B it can be observed that
the difference in performance between the GAMLSS and the distributional forest models as
seen in the single evaluation evens out, hence the specific choice of learning years seems
to have an impact as well.

@@

\begin{review}
The authors have well addressed the reviewers' comments. The two added supplementary 
materials give a more solid ground to the proposed post-processing method by showing 
it is robustness to some choice of forecast distribution and that the results presented 
in the main manuscript does not hold only for the specific station.
I recommend the paper to be accepted after the minor revisions proposed
hereafter have been addressed.
\end{review}

@@

Thank you very much for your feedback and the constructive comments regarding the paper. 
You are right that it still has to be tested how distributional trees and forests perform when
employing very complex distributions such as the Dagum distribution. 
However, contrary to the uncensored Gaussian distribution the parameters of the here applied 
censored Gaussian distribution are not orthogonal as changing the mean also influences the variance,
especially close-by the censoring point. Moreover, the three-parametric two-part hurdle model
employed in Supplement A is almost equivalent to the zero-inflated model you suggested. 
Hence, the distributional trees and forests have been tested for distributions with dependencies
among their parameters and have shown to perform well. But of course further investigation is
required in order to confirm these findings in general. This is now also mentioned in an additional 
subsection of the discussion in the manuscript.
